Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2017-06-13 cbm-rbd-paper.tex
typos, user license for sharing of accepted manuscript

\documentclass[authoryear]{elsarticle}

@@

While we also use a Bayesian approach with conjugate priors to provide exact expressions for the RLD,
one of the main differences between \citet{2013:si-et-al} and our paper
is that we use component status data and the system reliability block diagram instead of a continuous degradation signal
as basis for calculating the system RLD.
Another main difference is that our policy can be applied to arbitrary system configurations
(i.e., arbitrary reliability block diagrams with arbitrary components),
whereas the method given by \citet{2013:si-et-al} can only be applied to single components.
A third difference concerns how the cost rate is calculated.
\citet{2013:si-et-al} calculate this rate using the renewal-reward theory approximation.
Essential for using the renewal-reward theory for calculating the expected cost per unit of time
is that the relevant characteristics of the system considered and its environment are not changing,
i.e.\ that the failure behavior of the system,
in essence its relibability function, does not change over time,
and that the same policy with the same parameter values is used for a statistically long enough period of time.
However, due to the update method related to the CBM policy presented in this paper, %like in \citet{2013:si-et-al},
we cannot use the renewal-reward theory based calculation method,
and therefore use the exact formula for the average cost per unit of time.

@@

There are several aspects in our modelling that warrant further investigation.
In this paper, we assume that component failure times are observed precisely via monitoring.
However, in many applications, the component status can only be determined
at inspections, leading to interval-censored failure time observations.
Extending the model to account for interval-censored failure times
would allow to derive a condition-based maintenance policy with wider-spaced inspections
by determining the optimal moment for the next inspection of the system.
%which could also determine the optimal moment for the next inspection of the system.
%*** extend the model for inspection-based CBM (if no repair necessary, find optimal timing of next inspection),
%we would need to add interval-censored data (failure has happened between last and current inspection)

@@

As mentioned at the end of Section~\ref{sec:costrate},
we currently disregard the possibility of common cause failures,
i.e., simultaneous failures with a shared root cause.
Common cause failures can drastically reduce the system reliability
by leading to sudden system failures.
To offer a realistic estimation of the optimal time to maintenance $\tausnow$,
the system RLD $\Rsys(t)$ needs to account for such failures when they are possible.
%This needs to be implemented on the level of component models,
%specifically $P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big)$ 
%(not a product anymore if common-case failures can affect several component types at once).
When common cause failures can affect several component types at once,
the joint posterior predictive probabilities $P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big)$ in \eqref{eq:sysrel-survsign}
cannot be obtained as a product of component posterior predictive probabilities any more.
We think that by combining ideas from \cite{2015:coolen-coolen-maturi} and \cite{Troffaes2014a},
the proposed policy could be extended to accomodate common cause failures.

@@

\section*{Acknowledgements}

>>>>

\documentclass[authoryear]{myelsartcl}

@@

While we also use a Bayesian approach with conjugate priors to provide exact expressions for the RLD,
one of the main differences between \citet{2013:si-et-al} and our paper
is that we use component status data and the system reliability block diagram instead of a continuous degradation signal
as basis for calculating the system RLD.
Another main difference is that our policy can be applied to arbitrary system configurations
(i.e., arbitrary reliability block diagrams with arbitrary components),
whereas the method given by \citet{2013:si-et-al} can only be applied to single components.
A third difference concerns how the cost rate is calculated.
\citet{2013:si-et-al} calculate this rate using the renewal-reward theory approximation.
Essential for using the renewal-reward theory for calculating the expected cost per unit of time
is that the relevant characteristics of the system considered and its environment are not changing,
i.e.\ that the failure behavior of the system,
in essence its reliability function, does not change over time,
and that the same policy with the same parameter values is used for a statistically long enough period of time.
However, due to the update method related to the CBM policy presented in this paper, %like in \citet{2013:si-et-al},
we cannot use the renewal-reward theory based calculation method,
and therefore use the exact formula for the average cost per unit of time.

@@

There are several aspects in our modeling that warrant further investigation.
In this paper, we assume that component failure times are observed precisely via monitoring.
However, in many applications, the component status can only be determined
at inspections, leading to interval-censored failure time observations.
Extending the model to account for interval-censored failure times
would allow to derive a condition-based maintenance policy with wider-spaced inspections
by determining the optimal moment for the next inspection of the system.
%which could also determine the optimal moment for the next inspection of the system.
%*** extend the model for inspection-based CBM (if no repair necessary, find optimal timing of next inspection),
%we would need to add interval-censored data (failure has happened between last and current inspection)

@@

As mentioned at the end of Section~\ref{sec:costrate},
we currently disregard the possibility of common cause failures,
i.e., simultaneous failures with a shared root cause.
Common cause failures can drastically reduce the system reliability
by leading to sudden system failures.
To offer a realistic estimation of the optimal time to maintenance $\tausnow$,
the system RLD $\Rsys(t)$ needs to account for such failures when they are possible.
%This needs to be implemented on the level of component models,
%specifically $P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big)$ 
%(not a product anymore if common-case failures can affect several component types at once).
When common cause failures can affect several component types at once,
the joint posterior predictive probabilities $P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big)$ in \eqref{eq:sysrel-survsign}
cannot be obtained as a product of component posterior predictive probabilities any more.
We think that by combining ideas from \cite{2015:coolen-coolen-maturi} and \cite{Troffaes2014a},
the proposed policy could be extended to accommodate common cause failures.

@@

\section*{Acknowledgments}
